---
title: "Stackoverflow"
author: "HuzaifahZia,Junaid"
date: "10/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## loading libraries
```{r}
library(stackr)
library(dplyr)
```
## extracting data
```{r}
answers <- stack_users(712603, "answers", num_pages = 10, pagesize = 100)
```
## converting data to table data frame
```{r}
answers <- tbl_df(answers)
```
## displaying data
```{r}
answers
```
## API functions

#' Query answers from the Stack Exchange API
#'
#' Query for a list of answers, or information related to a one or more
#' specific answers.
#'
#' @param id A vector containing one or more answer IDs, or none to query
#' all answers
#' @param special If \code{"comments"}, return the comments on the answers
#' rather than the answers themselves
#' @template api_options
#'
#' @return A \code{data.frame} of answers.
#'
#' @template type_answer
#'
#' @export

```{r}
stack_answers <- function(id = NULL, special = NULL, ...) {
  url <- combine_url("answers", id, special, c("comments", "questions"))
  stack_GET(url, ...)
}
```
##  Mean accepted
```{r}
mean(answers$is_accepted)
```
## Top users Tags
```{r}
top_tags <- stact_users(712603,"top-answer-tags", pagesize = 100)
top_tags
```
## Graph
```{r}
top_tags %>% mutate(tag_name = reorder(tag_name,-answer_score)) %>% head(20) %>%
  ggplot(aes(tag_name,answer_score))+ geom_bar(stat = "identity")
```

