---
title: "Prctice from14-24"
author: "Muhammad Huzaifah Zia"
date: "10/12/2021"
output: pdf_document
---
## Subsetting And Sorting - Using Dates
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Subsetting and Sorting
## Setting seed for reproducible result from the random int generated by sample
```{r seed}
set.seed(13435)
```
## making a data frame with 3 columns 
## shuffling the rows usinng sample
## and making the 1st and 3rd elements of var2 column NA
## displaying x
```{r}
x <- data.frame("var1" = sample(1:5), "var2" = sample(6:10), "var3" = sample(11:15))
x <- x[sample(1:5),]; x$var2[c(1,3)] =NA
x
```
## Displaying column 1 of the dataframe x
## subsetting based on column
```{r}
x[,1]
```
## Displaying column where column = "var1" of dataframe x
## subsetting data based on column
```{r}
x [,"var1"]
```
## Displaying rows 1 to 2 of where column = "var2" of dataframe x
```{r}
x [1:2,"var2"]
```
## subsetting x by logical comparisons 
```{r}
x[(x$var1 <= 3 & x$var3 > 11),]
```

```{r}
x[(x$var1 <= 3 | x$var3 > 15),]
```
## subsetting by NAs
```{r}
x[which(x$var2 > 8),]
```
## sorting data
```{r}
sort(x$var1)
```

```{r}
sort(x$var2, na.last = TRUE)
```
## sorting by order
```{r}
x[order(x$var1),]
```

```{r}
x[order(x$var1, x$var3),]
```
## ordering with plyr
```{r}
library(plyr)
arrange(x,var1)
```

```{r}
arrange(x,desc(var1))
```
## Adding rows and columns
```{r}
x$var4 <- rnorm(5)
x
```

```{r}
Y <- cbind(x,rnorm(5))
Y
```
## --*--
## Summarizing data
## Fetching data from web
```{r}
if (!file.exists("./data")){
  dir.create("./data")
}
fileUrl <- "https://data.baltimorecity.gov/api/views/k5ry-ef3g/rows.csv?accessType=DOWNLOAD"
download.file(fileUrl,destfile="./data/restaurants.csv", method = "curl" )
restData <- read.csv("./data/restaurants.csv")
```
## lookat a bit of data
```{r}
head(restData,n=3)
```